---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# flexdb-tutorial

 [`flexdashboard`](https://pkgs.rstudio.com/flexdashboard/index.html) is an R package for combining visualizations (tabular and graphical) into flexible dashboards. This tutorial will demonstrate the ease of use in building complex layouts through a series of examples. flexdashboard works great with both base R graphics and ggplot, but it really shines when working with other visualization libraries. Specifically:
 
- JavaScript  visualizations with the [`htmlwidgets` package](https://www.htmlwidgets.org/)

- Tabular data with the [DT package](https://rstudio.github.io/DT/).

- Value boxes (`flexdashboard::valuebox()`)for highlighting important summary data .

- Gauges (`flexdashboard::gauge()`)for displaying values on a meter within a specified range.

- Maps through the leaflet package

- The bslib package for adding bootstrap/css styling. 


This repository contains a series of .Rmd files demonstrating a good selection of the variety that is available through flexdashboard. Just follow along with this README file to know which .Rmd file to use to see the specified flexibility. 


## Using `flexdashboard`

flexdashboard is used via Rmarkdown files (.Rmd) as an output option. In the YAML metadata at the top of the document, simply specify:

````
---
title: "My Dashboard"
output: flexdashboard::flex_dashboard
---
````


### Layouts 


A panel in flexdashboard is an area you can place a plot, a table, or some descriptive text. These are created with the use of 3 hashtags (`###`). By default, flexdashboard has a column based orientation. You can start a new column by using the level 2 markdown header (a series of hyphens)

See the .Rmd files in the `layout-examples` folder for examples of the different layout possibilities, including

1. flex rows
2. flex columns
3. scrolling
4. tab panels
5. multiple pages
6. story boards


### Widgets

The htmlwidgets package extends R graphics to JavaScript visualization packages. Visualizations designed with javascript give an extra level of user interactivity. In addition these visualizations can be resized on the fly to fit perfectly in your dashboard display.

See the examples in the the widget-examples folder

1. dygraph
2. leaflet and datatable
3. valueboxes and gauges


### Styling and themes

The folder (styling) has examples for adding and altering a navigation bar, adding links to external pages, and changing the visual theme of the dashboard. 

A large variety of bootswatch themes can be used to later the appearance of your dashboard. 

```{r}
themes <- c('default', 'cosmo', 'bootstrap', 'cerulean',
            'journal', 'flatly', 'readable', 'spacelab',
            'united', 'lumen', 'paper', 'sandstone', 'simplex',
            'yeti')
```

In addition, you can use the bslib package to gain the flexibility of modern css frameworks like bootstrap 5. 

